NFC and burnout in teachers - A replication and extension study

### 2021-09-13 Manuscript/Manuscript.Rmd
added table for metric descriptives

    isnorm_test <- mvn(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","covb")],
                       mvnTest = "mardia", covariance = TRUE, desc = TRUE, univariateTest = "SW")

@@

    desc_met <- data.frame(value = c("mean","sd","skewness","kurtosis","normality"),
                           mbi = rep(0,5),
                           mbi_ee = rep(0,5), mbi_dp = rep(0,5), mbi_rpe = rep(0,5),
                           erq = rep(0,5),
                           erq_supp = rep(0,5), erq_reap = rep(0,5),
                           scs = rep(0,5),
                           ncs = rep(0,5),
                           covb = rep(0,5))

    desc_met[1,2:ncol(desc_met)] <- isnorm_test$Descriptives$Mean
    desc_met[2,2:ncol(desc_met)] <- isnorm_test$Descriptives$Std.Dev
    desc_met[3,2:ncol(desc_met)] <- isnorm_test$Descriptives$Skew
    desc_met[4,2:ncol(desc_met)] <- isnorm_test$Descriptives$Kurtosis
    desc_met[5,2:ncol(desc_met)] <- isnorm_test$univariateNormality$Normality

@@

  desc_table <-
  kbl(correlations,
      booktabs = T, # no vertical lines
      escape = F, # correctly print special characters
      align = rep("l",11)) %>% # right aligns the text in every column except for the first
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = F, # correctly print special characters
             threeparttable = T) # line breaks in the footnote

@@

`r desc_table`

>>>>

    isnorm_test <- mvn(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")],
                       mvnTest = "mardia", covariance = TRUE, desc = TRUE, univariateTest = "SW")

@@

    desc_met <- data.frame(Variable = c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","DTH","DTL","DRF","COV"),
                           Minimum = sapply(score_data[,c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")], min),
                           Maximum = sapply(score_data[,c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")], max),
                           Mean = isnorm_test$Descriptives$Mean,
                           SD = isnorm_test$Descriptives$Std.Dev,
                           Normality = isnorm_test$univariateNormality$Normality,
                           Skewness = isnorm_test$Descriptives$Skew,
                           Kurtosis = isnorm_test$Descriptives$Kurtosis)
    # Drop the row names

    rownames(desc_met) <- NULL

    # Replace the capital YESes and NOs with small ones

    desc_met$Normality[grep("NO", desc_met$Normality)] <- "No"
    desc_met$Normality[grep("YES", desc_met$Normality)] <- "Yes"

    # Round the values

    desc_met[ ,c("Mean","SD","Skewness","Kurtosis")] <- round(desc_met[ ,c("Mean","SD","Skewness","Kurtosis")], digits = 2)

    # Put the information in a table

    met_table <-
      kbl(desc_met,
      booktabs = T, # no vertical lines
      escape = F, # correctly print special characters
      align = rep("r",8)) %>% # right aligns the text in every column except for the first
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation. \\\\textit{N} = 180.",
             escape = F, # correctly print special characters
             threeparttable = T) # line breaks in the footnote

@@

  desc_table <-
  kbl(correlations,
      booktabs = T, # no vertical lines
      escape = F, # correctly print special characters
      align = rep("l",14)) %>% # right aligns the text in every column except for the first
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = F, # correctly print special characters
             threeparttable = T) %>% # line breaks in the footnote
  kableExtra::landscape() # make the table horizontal

@@

Correlations and internal consistencies are displayed in **Table 1**.
`r desc_table`
